---
title: "FIFA Analysis"
author: "/Yihan Zhou"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---



Abstract {data-navmenu="About"}
==================
### **Abstract**

The project is focuses on FIFA world cup analysis mainly by data visualization, especially on the information of matches results in the history, playing attributes of all players of FIFA 18 and related English tweets during FIFA 18, too. 

Multiple types of visulizations would be achieved:

 1. Explanatory Data Analysis
 
    - 
   
 2. Geographical Visualization
 
 3. Network Visualization
 
 4. Time series
 
 5. Text Visualization 

Through the aboved visulization analysis, many possible explorations are completed：

For example, the co-related between age and potential of players; is there a pattern in the results of competition over the years; which group pays the most attention to this prestigious football tournament. Further, combining the information of players and historical results, we could infer if there is particular strength could detemine the team's victory.


Datasets Introduction {data-navmenu="About"}
==================
### **Datasets Introduction**

The project uses 3 multiple datasets from Kaggle. The link and details descriptions are shown below.

Dataset 1 - "FIFA18 Complete Player Dataset"

 - Link: https://www.kaggle.com/thec03u5/fifa-18-demo-player-dataset?select=CompleteDataset.csv (combining several csvs from link together)
 
 - Details: It includes every players' personality, attributes and playing position data(???) featuring in FIFA 18
 
 - Columns: 
 
   - Player index number 
  
   - Name of a player
  
   - Age of a player
  
   - Player nationality 
   
   - Player's overall score
  
   - Player's potential score
  
   - Acceleration score
   
   - Aggression score
   
   - Agility score
   
   - Balance score
   
   - Ball control score
   
   - Composure score
   
   - Crossing score
   
   - Curve score
   
   - Dribbling score
   
   

Dataset 2 - "FIFA World Cup Matches"

 - Link: https://www.kaggle.com/abecklas/fifa-world-cup?select=WorldCupMatches.csv (using the first csv from link)
 
 - Details: It shows all information about the World Cups Matches from 1930 to 2014
 
 - Columns:
 
   - The year in which the match was playered
   
   - The date on which the match was playered
  
   - The city where the match was playered
   
   - Home team country name
   
   - Away team country name
   
   - Win conditions
 
 
Dataset 3 - "FIFA18 Tweets Collection"

 - Link: https://www.kaggle.com/rgupta09/world-cup-2018-tweets 
 
 - Details: It contains a random collection of 530k English language tweets starting from the Round 16 till the Final of FIFA 18
 
 - Columns: 
 
   - Unique ID of the tweet
   
   - Timestamp when it was tweeted
   
   - The length of the tweet
   
   - The content of the tweet
   
   - The number of likes received by the tweet
   
   - The number of shared times
   
   - The hashtags found in the tweet



Exploratory Data Analysis
=====================================

Inputs {.sidebar}
-------------------------------------


11111


   
Row {.tabset .tabset-fade}
-------------------------------------

### Chart 1
```{r}

```

### Chart 2
```{r}

```


Geographical Visualization
=====================================     

Inputs {.sidebar}
-------------------------------------

22222


Row
-------------------------------------

### Chart 1
    
```{r}
```


### Chart 2 

```{r}

```

Network
=====================================
Inputs {.sidebar}
-------------------------------------

33333

Row
-------------------------------------

### Chart 1


Time Series
=====================================  
Inputs {.sidebar}
-------------------------------------
44444



Row
-------------------------------------
### Chart 1
```{r}

```


Text Visualization
=====================================
Inputs {.sidebar}
-------------------------------------
55555


Row
-------------------------------------
### Chart 1
```{r}

```